%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
%\usepackage{color}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Fan Bu}
\address{fbu@umich.edu}
\address{https://fanbu1995.github.io}

%% maybe highlight some stuff for things done in the past year...
%\newcommand{\thisYear}[1]{
%	\colorbox{gray!30}{\parbox{17cm}{#1}}
%}
\newcommand{\thisYear}[1]{
	#1
}

%% command to highlight my authorship
%% can switch between bold or underscore...
\newcommand{\myName}[1]{
	\textbf{#1}
}
%\newcommand{\myName}[1]{\underline{#1}}

%% Header of file
% \usepackage{fancyhdr}
% \pagestyle{fancy}
% \fancyhf{}
% \renewcommand{\headrulewidth}{0pt}
% \rhead{}
% \lhead{Bu, Fan - CV}

\begin{document}

% work/affiliations section

\begin{rSection}{PROFESSIONAL AFFILIATIONS}
	
{\bf Tenure-track Assistant Professor} \hfill {\em Jan 2024  -  present} 
\\ {\small Department of Biostatistics, University of Michigan - Ann Arbor}
	
{\bf Postdoctoral Scholar} \hfill {\em Aug 2021 - Dec 2023} 
\\ {\small Department of Biostatistics, University of California - Los Angeles}
\\ {\small Supervisor: Dr. Marc Suchard}

{\bf Visiting Scholar} \hfill {\em Sept 2022 - Nov 2022} 
\\ {\small Simons Institute, University of California - Berkeley}


{\bf Research Intern} \hfill {\em May 2020 - Aug 2020} 
\\ { \small Duke Center for AIDS Research}
\end{rSection}

\begin{rSection}{EDUCATION}
{\bf Department of Statistical Science, Duke University} \hfill {\em 2017 - 2021} 
\\ Ph.D. in Statistics; Dissertation: Stochastic Process Models on Dynamic Networks
\\ {\small Advisor: Dr. Alexander Volfovsky}

{\bf School of Mathematical Sciences, Peking University} \hfill {\em 2013 - 2017} 
\\ B.S. in Mathematics and Applied Mathematics
\end{rSection}

%\begin{rSection}{RESEARCH INTERESTS}
%
%Bayesian statistics and statistical computation for complex and large-scale datasets; stochastic processes and dynamic models; observational healthcare studies and 
%%health data science and 
%informatics; computational social science. %With applications in observational health data analysis, infectious disease modeling, social sciences, and sports analytics.
%
%\end{rSection}

% \begin{rSection}{Skills}

% \textbf{Programming Languages}: R, Python, MATLAB, SQL, Julia.

% \textbf{Languages}: Mandarin (native) and English (proficient).

% \end{rSection}


\begin{rSection}{PUBLICATIONS \& PREPRINTS}
%{\footnotesize{($\dagger$ denotes first-author work)}}

{\footnotesize $\dagger$ denotes student mentee}

\hspace{-.2in} \textbf{Statistical Methodology:}

N. Hartman and \myName{F. Bu}. Joint Models for Health Services Delivery During Infectious Disease Epidemics (2025+). \emph{Under review}. 

\smallskip 

P. Chatha$^\dagger$, \myName{F. Bu}, J. Regier, E. Snitkin, and J. Zelner. 
Neural Posterior Estimation for Stochastic Epidemic Modeling (2025+). \emph{Under revisions}.	%\textit{arXiv:2412.12967}

\smallskip

\thisYear{
\myName{F. Bu}, A. E. Aiello, A. Volfovsky, and J. Xu.  
Stochastic EM algorithm for partially observed stochastic epidemics with individual heterogeneity (2025).  \emph{Biostatistics}.%$^\dagger$
}

\smallskip

\myName{F. Bu}, J. Kagaayi, M. K. Grabowski, J. Xu, and O. Ratmann.
Inferring HIV Transmission Patterns from Viral Deep-Sequence Data via Latent Spatial Poisson Processes (2024). \emph{Biometrics.} 
(Winner of 2024 ISBA Biostats and Pharma Best Paper Award.)

\smallskip

\myName{F. Bu}, M. J. Schuemie,  A. Nishimura, L. H. Smith, K. Kostka, T. Falconer, J. A. McLeggon, P. B. Ryan, G. Hripcsak, and M. A. Suchard.
Bayesian Safety Surveillance with Adaptive Bias Correction (2023). \emph{Statistics in Medicine.} %$^\dagger$

\smallskip


M. Schuemie, \myName{F. Bu}, A. Nishimura and M. Suchard.
Adjusting for Both Sequential Testing and Systematic Error in Safety Surveillance using Observational Data: Empirical Calibration and MaxSPRT (2023). \emph{Statistics in Medicine.}
%arXiv:2207.02704 }

\smallskip


\myName{F. Bu}, A. E. Aiello, J. Xu, and A. Volfovsky. 
Likelihood-based Inference for Partially Observed Epidemics on Dynamic Networks (2020). \emph{Journal of the American Statistical Association} (Winner of 2020 ASA SBSS Student Paper Award.) %$^\dagger$

\smallskip

\myName{F. Bu}, S. Xu, K. Heller, and A. Volfovsky. 
SMOGS: Social Network Metrics of Game Success (2019). \emph{The 22nd International Conference on Artificial Intelligence and Statistics (AISTATS)}. %$^\dagger$

\smallskip

W. Zhang, \myName{F. Bu}, D. Owen-Oas, K. Heller, and X. Zhu. 
Who Started It? Identifying Root Sources in Textual Conversation Threads (2018). \emph{arXiv:1809.03648}.
%\smallskip 

\medskip

%\newpage 
\hspace{-.2in} \textbf{Scientific / Collaborative:}

S. Chattopadhyay, \myName{F. Bu}, M. J. Schuemie, J. A. McLeggon, E. Westlund, G. Hripcsak, P. Ryan, M. A. Suchard. 
Comparative performance of the concurrent comparator design with existing vaccine safety surveillance approaches on real-world observational health data (2025+). \emph{Under review}. 

\smallskip 

C. Kim, \myName{F. Bu}, C. Blacketer, A. Ostropolets, [...], and Y. Lu. Comparative safety of second-Line antihyperglycemic agents in older adults with type 2 diabetes: a multinational real-world evidence from LEGEND-T2DM (2025+). \emph{Under review}.  

\smallskip

C. Reyes, T. Duarte-Salles, A. Pistillo, \myName{F. Bu}, [...], and M. A. Suchard. Gastrointestinal Adverse Effects of Second-Line Anti-Diabetic Drugs: A Federated Cohort Study (2025+). \emph{Under revisions}. 

\smallskip 

L. Rountree$^\dagger$, G. Tong, \myName{F. Bu}, M. Ranney, and B. Mukherjee. Association of COVID-19 outcomes with measures of institutional and interpersonal trust: An ecological analysis using national data from 61 countries (2025). \emph{Nature Scientific Reports}.   

\smallskip 

V. Obregon-Perko, A. Awasthi, R. Barfield, [...], \myName{F. Bu}, [...], and A. Chahroudi. Biomarkers for viral rebound timing and control post-ART in SHIV-infected infant macaques (2025). \emph{Science Translational Medicine} (accepted with minor revisions).

\smallskip 

D. Morales, \myName{F. Bu}, B. Viernes, [...], and M. A. Suchard. Risk of thyroid tumours with glucagon-like peptide-1 receptor agonists: international cohort study (2025). \emph{Diabetes Care.} 

\smallskip 

L. Rountree$^\dagger$, Y.T.  Lin, C. Liu, M. Salvatore, A.  Admon, B. K. Nallamothu, K. Singh, A. Basu, \myName{F. Bu}, B. Mukherjee. Reporting of Fairness Metrics in Clinical Risk Prediction Models: A Call for Change to Ensure Equitable Precision Health Benefits for All (2025). \emph{Online Journal of Public Health Informatics}.

\smallskip 

C. Cai, M. Hribar, Sally Baxter, [...],  \myName{F. Bu}, [...], and Patrick B. Ryan. 
Semaglutide and Nonarteritic Anterior Ischemic Optic Neuropathy (2025). \emph{JAMA Ophthalmology}.  

\smallskip

\myName{F. Bu}, E. Minty, A. Aminorroaya, C. Blacketer, [...], and M. A. Suchard. 
Multi-national Patterns of Individual Cardioprotective Agents as Second-line Treatments for Type 2 Diabetes Mellitus: a LEGEND-T2DM Study (2024). \emph{Proceedings of the 2025 OHDSI Global Symposium.}

\thisYear{
R. Khera, A. Aminorroaya, L. S. Dhingra, P. M.  Thangaraj, A. P. Camargos, \myName{F. Bu}, [...], and M. A. Suchard. Comparative Effectiveness of Second-line Antihyperglycemic Agents for Cardiovascular Outcomes: A Large-scale, Multinational, Federated Analysis of the LEGEND-T2DM Study (2024). \emph{Journal of the American College of Cardiology}. 
}

\smallskip 

C. Cai, A. Nishimura, M. Bowring, [...], \myName{F. Bu}, [...], and Patrick B. Ryan. Similar risk of kidney failure among patients with blinding diseases who receive ranibizumab, aflibercept, and bevacizumab (2024). \emph{Ophthalmology Retina}.

\smallskip 

\myName{F. Bu}, F. Arshad, G. Hripcsak, P. B. Ryan, M. J. Schuemie, and M. A. Suchard. Response to Comments on ``Serially Combining Epidemiological Designs Does Not Improve Overall Signal Detection in Vaccine Safety Surveillance'' (2024). \emph{Drug Safety}. 

\smallskip 

T. V. Anand, \myName{F. Bu}, M. J. Schuemie, M. A. Suchard, and G. Hripcsak. Comparative safety and effectiveness of angiotensin converting enzyme inhibitors and thiazides and thiazide-like diuretics under strict monotherapy (2024).  \emph{Journal of Clinical Hypertension}.

\smallskip 

R. Khera, L.S. Dhingra, A. Aminorroaya, [...], \myName{F. Bu}, [...], and  M. A. Suchard.  Multinational patterns of second line antihyperglycaemic drug initiation across cardiovascular risk groups: federated pharmacoepidemiological evaluation in LEGEND-T2DM (2023). \emph{BMJ medicine}. 

\smallskip

F. Arshad, M. J. Schuemie, \myName{F. Bu}, [...], and M. A. Suchard. Serially Combining Epidemiological Designs Does Not Improve Overall Signal Detection in Vaccine Safety Surveillance (2023). \emph{Drug Safety}. 

\smallskip

E. A. Voss, A. Shoaibi, L. Y. H. Lai,  [...], \myName{F. Bu}, [...], and P. B. Ryan. Contextualising adverse events of special interest to characterise the baseline incidence rates in 24 million patients with COVID-19 across 26 databases: a multinational retrospective cohort study (2023). \emph{EClinicalMedicine}. 


\smallskip

R. Asencio, \myName{F. Bu}, L. Tucker, G. Varela, J. Moody, and A. Volfovsky. 
Network Position and Emergent Phenomena: A Multi-team System Case Study (2022+). \emph{Under revisions.}


\end{rSection}

%\newpage

%\begin{rSection}{Working Papers}

% will add to this section later on

% \smallskip
%
%V. Obregon-Perko, A. Awasthi, \textbf{F. Bu}, R. Barfield, S. J. Berendam, B. Yagnik,  T. Styles, M. Kumar, E. Fray, J. Siliciano, R. R. Amara, G. G. Fouda, S. R. Permar, C. Chan, A. Chahroudi. 
%Viral and Immune Predictors of Time to Viral Rebound in SHIV-infected Infant Macaques (2021+).
%\end{rSection}

%\newpage

\begin{rSection}{AWARDS \& HONORS}

2024 ISBA Biostats and Pharma Best Paper Award. \hfill {\em February 2025}

\vspace{-0.1in}
{\footnotesize For ``Inferring HIV Transmission Patterns from Viral Deep-Sequence Data via Latent Spatial Poisson Processes''}


Blackwell-Rosenbluth Award (for outstanding early-career statisticians) \hfill {\em November 2024}

\vspace{-0.1in}

\thisYear{
by the International Society for Bayesian Analysis. 
}

	
OHDSI Best Collaborator Showcase for clinical application (nominated).
\hfill {\em October 2024}

OHDSI Titan Award for Methodological Research. 
\hfill {\em October 2022}

Mentorship of Excellence award for 2022 UCLA B.I.G. summer research program. \hfill {\em August 2022}

ISBA World Meeting travel award.
\hfill {\em June 2022}

Duke CFAR Fall Retreat Best Poster Award. 
\hfill {\em October 2020}

American Statistical Association Section on Bayesian Statistical Science (ASA SBSS)
%SBSS Student Paper Award; JSM travel award. 
\hfill {\em August 2020}

\vspace{-0.1in}
Student Paper Award. 

\vspace{-0.1in}
{\footnotesize For ``Likelihood-based Inference for Partially Observed Epidemics on Dynamic Networks''}

Joint Statistical Meetings travel award. \hfill {\em August 2020}

Honorable Mention for Ph.D. Teaching Assistant for the Year. 
\hfill {\em May 2020}

%\textit{December 2017}.
Women in Machine Learning Workshop (WiML) travel award. \hfill {\em December 2017}

\end{rSection}

\begin{rSection}{RESEARCH GRANTS \& AWARDS}
	

	\hspace*{-0.25in} 
	US FDA CBER BEST Initiative,  75F40120D00039    \hfill{\em Sep 2024 - March 2025}
 \\
	``OHDSI-based FDA BEST Community Engagement and Development Coordination Center'' \\
	Role: UM site PI (lead PI: George Hripcsak, Columbia University)
	\medskip 
	
	\hspace*{-0.25in} 
		Bill \& Melinda Gates Foundation, INV-077867     \hfill{\em Aug 2024 - Aug 2026}
			 \\
	``Comparative Effectiveness of Different Dosing Schedules of PCV in Brazil'' \\
	Role: UM site PI (lead PI: Kayoko Shioda, Boston University)
	
		\medskip 
	
	\hspace*{-0.25in} 
	MIDAS Propelling Original Data Science (PODS) program \hfill{\em Aug 2024 - July 2025} 
	\\
	``Neural Posterior Estimation (NPE) approaches for fitting high-dimensional stochastic epidemic models to real-world spatiotemporal disease data'' \\
	Role: dual PI (with Jon Zelner, University of Michigan)
	
	\medskip 
	
	\hspace*{-0.25in}
	US CDC NCIRD U01, IP001138 \hfill{\em Jan 2025 - Aug 2025} 
	\\
	
	``Data driven transmission models to optimize influenza vaccination and pandemic mitigation strategies'' \\
	Role: co-I (PI: Jon Zelner, University of Michigan)
	
\end{rSection}


%\newpage

\begin{rSection}{PROFESSIONAL SERVICE}
	
	\hspace*{-0.2in}\textbf{Professional Societies:}
	
	Program Chair for \emph{Biopharmaceutical section of the International Society} \hfill {\em January 2025 - present}


	\vspace{-0.1in}
	\emph{for Bayesian Analysis}.

	
	\thisYear{
	Associate Chair for \emph{ENAR Social Media Committee}  \hfill {\em September 2023 - December 2024}
}

		\smallskip
	
	Program Chair for \emph{the junior section of the International Society} \hfill {\em January 2022 - December 2023}
	
	\vspace{-0.1in}
	\emph{for Bayesian Analysis (j-ISBA)}.
	
\medskip 

 \hspace*{-0.2in}\textbf{Editorial and Review Responsibilities:}

 Member for Book of OHDSI Committee. \hfill{\em March - December 2025}
 
 	Judge for ASA SBSS student paper competition. 	 \hfill {\em October - December 2024}
 	
 	Scientific Review Committee member for 2024 OHDSI Global Symposium. 	\hfill {\em March - October 2024}
 	
 	\smallskip 
	
 Co-editor for BaYSM 2023 proceedings, ``\emph{New trends in Bayesian Statistics}''.	\hfill {\em May - December 2024}

    \smallskip 
    
 
    Grant proposal reviewer for UKRI.	\hfill {\em February 2024}

    
    \smallskip 
    
    \textbf{Journal reviewer} for: \emph{The Proceedings of the National Academy of Sciences (PNAS)}, \emph{Nature Communications}, \emph{Nature Cardiovascular Research}, \emph{Journal of the American Statistical Association (JASA)}, \emph{Biometrics}, \emph{Annals of Applied Statistics (AOAS)}, \emph{Journal of Computational and Graphical Statistics (JCGS)}, \emph{Statistics in Medicine}, \emph{Biostatistics}, \emph{Bayesian Analysis},  \emph{Statistical Science}, \emph{Communications in Statistics},  \emph{Science Advances}, \emph{Environmental and Ecological Statistics}, \emph{Statistics and Public Policy},  and \emph{Statistics and Computing}. 
    
 \smallskip 
%    
    \textbf{Conference reviewer} for: \emph{Uncertainty in Artificial Intelligence (UAI) 2024}. 
    
    \medskip 

 \hspace*{-0.2in}\textbf{Conference Organization:}
 
 \thisYear{
 	Scientific Programme Committee member for CFE-CMStatistics 2025 \hfill {\em March - December 2025}
 }
 
 	\thisYear{
 Scientific Programme Committee member for CFE-CMStatistics 2024 \hfill {\em April - December 2024}
}
 
 	\thisYear{
 Organizing Committee member for BIRS-CMO Workshop	\hfill {\em December 2023 - September 2024}
 }
\vspace{-0.1in}
	\thisYear{
``Frontiers of Bayesian Inference and Data Science''. 
}

 
\smallskip 
 
	\thisYear{
Organizing Committee member for 2024 ISBA EAC conference. 	\hfill {\em February - June 2024}
}
	
\smallskip

	\thisYear{
Invited session (j-ISBA sponsored) organizer for  \hfill  {\em December 2023 - August 2024}
}

\vspace{-0.1in}
Joint Statistical Meetings (JSM) 2024


\smallskip
	
Organizing Committee member for Bayesian Young Statisticians  \hfill {\em May - November 2023}

\vspace{-0.1in}
Meeting (BaYSM) 2023.


 \hspace*{-0.2in}\textbf{Internal \& Miscellaneous: }
 
 Faculty judge for \emph{Michigan Student Symposium for Interdisciplinary}  \hfill {\em March 2025}


 \vspace*{-0.1in}
 \emph{Statistical Sciences (MSSISS)}

 
 Chair of seminar committee for UM Biostatistics. \hfill {\em September 2024 - August 2025}

 
 J-FAB committee member for UM School of Public Health.  \hfill {\em September 2023 - August 2025}

Judge for \emph{Duke Datathon}.  \hfill {\em October 2020 \& 2021}

% \smallskip

% Reviewer for \emph{Environmental and Ecological Statistics}. \hfill {\em October 2021}

% \smallskip

% %\textit{Jan 2020 \& August 2019}. 
% Reviewer for \emph{Science Advances}. \hfill {\em August 2019 - July 2021}

% \smallskip

% Reviewer for \emph{Journal of the American Statistical Association}. \hfill {\em June 2021} 

\smallskip

%\textit{April 2020}.
Consultant for \emph{DataFest: COVID-19 Virtual Data Challenge}.  \hfill {\em April 2020}

%\smallskip

%\textit{May-August 2019}.
% Team manager and student mentor for \emph{Duke Data+ 2019}. \hfill {\em May-August 2019}

\smallskip

%\textit{April 2018 \& April 2019}. 
Consultant for \emph{ASA DataFest @ Duke}. \hfill {\em April 2018 \& April 2019}
\end{rSection}

\begin{rSection}{TEACHING \& MENTORING}
	
\hspace*{-0.2in}\textbf{While at University of Michigan:}

Ph.D.  committee member for: 

\begin{quote}
	Prayag Chatta (Statistics), Leyao Zhang (Biostatistics),  Mingyan Yu (Biostatistics), Tasmine Clement (Bioinformatics), and Troy (Zirui) Zhou (Epidemiology). 
\end{quote}
	

    \emph{Biostatistics 602: Biostatistical Inference}.  \hfill {\em Winter 2025}


 \emph{Biostatistics 602: Biostatistical Inference}.  \hfill {\em Winter 2024}

\smallskip 

\hspace*{-0.2in}\textbf{While at UCLA:}
	
	Instructor for OHDSI Tutorials at the 2023 Global Symposium.  \hfill {\em Fall 2023}
		
	Mentor for the 2022 \emph{B.I.G. summer research program}.  \hfill {\em Summer 2022}
	
\smallskip 
	
\hspace*{-0.2in}\textbf{While at Duke University:}
	
	Instructor of Record for 
	
		\hspace{0.2in} \emph{STA101: Data Analysis/Statistical Inference} \hfill {\em Summer 2021}
	
	Lab instructor and teaching assistant for 
	
	\hspace{0.2in} \emph{STA199: Introduction to Data Science} \hfill {\em Fall 2020}
	
	\hspace{0.2in} \emph{STA723: Statistics Case Studies}. \hfill {\em Spring 2020}
	
	\hspace{0.2in} \emph{STA601: Bayesian Methods and Modern Statistics}. \hfill {\em Fall 2019}
	
	%\smallskip
	
	Team manager and student mentor for \emph{Duke Data+ 2019}. \hfill {\em Summer 2019}
	
	%\textit{August 2018}.
	Instructor of \emph{Duke Statistical Science Bootcamp}. \hfill {\em August 2018}
\end{rSection}

\begin{rSection}{INVITED TALKS \& PRESENTATIONS}
	
	\hspace{-.2in} {\textbf{Oral Presentations:}}
	
	Invited talk at CmStatistics 2025.  \hfill {\em December 2025 (scheduled)}
	
	Invited talk at EcoSta 2025. \hfill {\em August 2025 (scheduled)}
	
	Topic contributed talk at Joint Statistical Meetings. \hfill {\em August 2025}
	
	Invited talk at IMS New Researchers Conference (NRC). \hfill {\em August 2025}
	
	Invited talk at the ISBA BioPharm meeting.  \hfill {\em June 2025}
	
	Invited talk at the 14th International Conference on   \hfill {\em June 2025}
	
	\vspace*{-0.1in}
	Bayesian Nonparametrics. 
	
	Invited seminar talk at Statistics Department, UC Riverside.  \hfill {\em June 2025}
	
	Invited talk at 2025 Bayesian Young Statisticians Meeting (BaYSM). \hfill {\em April 2025}
	

	Invited seminar talk at Duke Biostatistics \& Bioinformatics.  \hfill {\em February 2025}

	

	Invited seminar talk at Centre for Statistics in Medicine (CSM)  \hfill {\em December 2024}


	\vspace{-0.1in} 
	Botnar Research Centre, Oxford University. 


	Invited talk at the UM Statistics student seminar.  \hfill {\em November 2024} 

	
	\thisYear{
	Invited talk at the Duke Statistical Science Alumni Symposium.  \hfill {\em October 2024} 
}
	
	Invited talk at the 2024 International Day of Women  in Statistics 
	 \hfill {\em October 2024} 
	
	\vspace{-0.1in} 
	and Data Science (IDWSDS) Conference. 
	
	\thisYear{
	Contributed talk at ISBA World Meetings 2024.  \hfill {\em July 2024}
}
	
	\thisYear{
	Invited talk at Ecosta 2024.  \hfill {\em July 2024}
}
	
	Invited talk at the Online Seminar on Spatial and spatio-temporal Point processes   \hfill {\em April 2024}
	
	\vspace{-0.1in} 
	and beyond (OSSP).
	
	Invited talk at the Statistical Methods for Infectious Diseases Across Scales Workshop \hfill {\em April 2024}
	
	\vspace{-0.1in}
	(by Penn State University).
	
	Recent publications highlight talk at OHDSI community meeting. \hfill {\em March 2024}
	
	Invited talk at ENAR 2024.  \hfill {\em March 2024}
	
	Invited talk at CMStatistics 2023. \hfill {\em December 2023}
	
	Invited talk at the RAND statistics seminar. \hfill {\em Nov 2023}
	
	Invited talk at EcoSta 2023. \hfill {\em August 2023}
	
	Invited talk at IISA 2023.  \hfill {\em June 2023}
	
	%Invited talk at WNAR 2023 (scheduled). \hfill {\em June 2023}
	%
	%Invited workshop presentation at Brin Mathematics Research Center  (scheduled). \hfill {\em April 2023}
	
	Contributed talk at ENAR 2023. \hfill {\em March 2023}
	
	Invited colloquim talk at Reed College. \hfill {\em March 2023}
	
	Invited talk at the FDA CBER BEST Seminar Series. \hfill {\em February 2023}
	
	Topic-contributed talk at CMStatistics 2022. \hfill {\em December 2022}
	
	Invited talk at the UCLA 2022 Fall Biomathematics Seminar Series . \hfill {\em November 2022}
	
	Invited presentation at the 2022 OHDSI Global Symposium.  \hfill {\em October 2022}
	
	{Oral presentation at NSF Student Conference on COVID-19 Modeling.} \hfill {\em January 2021}
	
	{Invited talk at 2020 Bayesian Young Statisticians Meeting: Online (BAYSM:O).} \hfill {\em November 2020}
	
	%\textit{August 2020}.
	{Topic-contributed talk at 2020 Joint Statistical Meetings. } \hfill {\em August 2020}
	
	%\textit{November 2019}.
	{Invited talk at the 3rd Annual AT\&T Labs Graduate Student Symposium.} \hfill {\em November 2019}
	
	%\smallskip
	
	%\textit{September 2019}.
	{Invited talk at the 2019 New England Symposium on Statistics in Sports} \hfill {\em September 2019}
	
	\vspace{-0.1in}
	(NESSIS).
	
	%\textit{March 2019}.
%	Spotlight talk on Duke Machine Learning Day. \hfill {\em March 2019}
	
	%\smallskip
	
	% {Oral landscape analysis presentation at the FDA CBER BEST collaborative meeting.} \hfill {\em October 2021}
	
	% {Highlight presentation on the LEGEND Initiative at the OHDSI } \hfill {\em October 2021}
	
	% \vspace{-0.1in}
	% Community Call.
	\medskip
	%\newpage
	
	\hspace*{-0.2in}\textbf{Poster Presentations:}
	
	Collaborator Showcase poster presentation at the 2024 OHDSI Global Symposium.  \hfill {\em October 2024}
	
	Poster presentation at the 2022 ISBA World Meeting. \hfill {\em June 2022}
	
	Poster presentation at the Dynamics \& Evolution of Human Viruses meeting.  \hfill {\em April 2022}
	
	%\smallskip
	
	Poster presentation at the 22nd International Conference on   \hfill {\em April 2019}
	
	\vspace{-0.1in}
	Artificial Intelligence and Statistics (AISTATS).
	
	%\smallskip
	
	%\smallskip
	
	%\textit{June 2018}. 
	Poster presentation at the 2018 ISBA World Meeting.\hfill {\em June 2018}
	
	%\smallskip
	Poster presentation at Women in Machine Learning Workshop (WiML) 2017.\hfill {\em December 2017}
	
\end{rSection}

%\pagebreak



%\newpage


%\begin{rSection}{Select Ongoing \& Past Research}



% Modeling HIV Transmission Flow From Viral Deep-sequencing Data: A Poisson Spatial Process Approach (2021+). (Ongoing work with Jason Xu and Oliver Ratmann.)

% \smallskip

% Autologous Virus Neutralizing Antibodies Delay Virus Rebound in Oral Infant Shiv
% Model (2021+). (Ongoing work with Stella J Berendam, Sallie Permar, Cliburn Chan, et al.)

% \smallskip

% Historical tone change from Middle Chinese to modern Beijing Mandarin: Usage-based phonology and modeling (2019+). (Ongoing work with Haowen Zhang and Maria Giavazzi, Ecole Normale Supérieure de Paris.)

% \smallskip

%
%Bayesian Methods Development for Sequential Monitoring of Observational Data for Vaccine Safety, under FDA's CBER BEST collaborative contract (2021+). \emph{Work in progress}.
%
%\smallskip
%
%
%The Evolution of Popularity and Images of Characters in Marvel Cinematic Universe Fanfictions (2018). (Technical report at \emph{arXiv:1805.03774})
%
%\smallskip
%
%Traffic Speed Nowcasting Based on Urban Road Network and Artificial Neural Network (2017). (B.S. thesis)
%
%\smallskip
%
%Detection of Differential Genetic Networks (2016). (Supported by the National Undergraduate Innovation Grant of China)
%
%
%\end{rSection}

\end{document}
